\thetitle

### 2020-11-18 sun_phases/spin_qudit_tomo.tex
simplified reconstruction error maximum
minor changes to reconsturction error maximization work
minor changes to text corrected a typo

The remainder of this section is devoted to defining the quantum error scale $\epsilon_V^2$ (derived in Appendix \ref{sec:error}), and can be skipped without consequence for the discussions in the rest of this paper.
To write out this error in full, we first rewrite the reconstruction error in Eq.~\eqref{eq:error} as
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \f1n \sum_\ell \sp{\bk{\chi_{V\ell}|\rho_\ell}
    - \bk{\rho_\ell|\N_{V\ell}|\rho_\ell}},
  \label{eq:error_simp}
\end{align}
where $\ket{\rho_\ell}\equiv\sum_m \rho_{\ell m}\ket{m}$, and similarly $\ket{\chi_{V\ell}}\equiv\sum_m \chi^V_{\ell m} \ket{m}$ is a vector of the scalars $\chi^V_{\ell m}$ defined by
\begin{align}
  \chi^V_{LM} &\equiv
  \sum_\ell \obk{\N_{V\ell}|\D_M|\I g_{L\ell}}, \\
  g_{L\ell} &\equiv \sum_{m,m'}
  \obk{T_{L,m+m'}|T_{\ell m}T_{\ell m'}} \op{m}{m'}, \\
  \I &\equiv \sum_m \p{-1}^m \op{-m}{m}, \\
  \D_M &\equiv \sum_{m,m'} \delta_{M,m'-m} \op{mm'}.
\end{align}
Here $g_{L\ell}$ is essentially a matrix of transition operator product coefficients (see Appendix \ref{sec:trans_prod}), and $\D_M$ simply picks off the $M$-th diagonal of the matrix it acts on.
Maximizing the reconstruction error in Eq.~\eqref{eq:error_simp} over all $\rho$ with $\tr\rho=1$ leads to the bound in Eq.~\eqref{eq:bound} with
\begin{align}
  \epsilon_V^2 \equiv \sum_\ell\sp{\bk{\chi_{V\ell}|\rho_{V\ell}^\star}
    - \bk{\rho_{V\ell}^\star|\N_{V\ell}|\rho_{V\ell}^\star}}
\end{align}
where the maximizers
\begin{align}
  \ket{\rho_{V\ell}^\star} \stackrel{\ell>0}{\equiv}
  \L_{V\ell}^{-1} \ket{\chi_{V\ell}},
  &&
  \ket{\rho_{V,0}^\star} \equiv \f1{\sqrt{d}} \ket{0},
\end{align}
are defined in terms of the inverse $\L_{V\ell}^{-1}$ of
\begin{align}
  \L_{V\ell} \equiv \N_{V\ell} + \I \N_{V\ell} \I.
\end{align}
Note that the bound in Eq.~\eqref{eq:bound} is obtained by maximizing the reconstruction error in Eq.~\eqref{eq:error_simp} over all possible $\rho$ (satisfying $\tr\rho=1$) regardless of their spectrum.
As a consequence, the maximizing ``state'' $\rho_V^\star$ may generally have negative eigenvalues.
In principle, there is therefore room for improvement on the bound in Eq.~\eqref{eq:bound} by maximizing reconstruction error over the (restricted) domain of states with a non-negative spectrum.

@@

  \ket{\chi_{V\ell}} - \L_{V\ell} \ket{\rho_{V\ell}^\star}

@@

  \L_{V\ell} \equiv \N_{V\ell} + \I N_{V\ell} \I,

@@

  \L_{V\ell}^{-1} \ket{\chi_{V\ell}},

@@

  = \f1n \sum_\ell \epsilon_{V\ell}^2,
  \epsilon_{V\ell}^2 \equiv \bk{\chi_{V\ell}|\rho_{V\ell}^\star}
  - \bk{\rho_{V\ell}^\star|\N_{V\ell}|\rho_{V\ell}^\star}.

@@

@@

In principle, there is therefore room for improvement on the bound in Eq.~\eqref{eq:bound_SM} by maximizing reconstruction error over the (restricted) domain of states with a non-negative spectrum.

>>>>

The remainder of this section is devoted to defining the quantum error scale $\epsilon_V^2$ (derived in Appendix \ref{sec:error}), and can be skipped without consequence for the discussions in the rest of this paper.
To write out this error in full, we first rewrite the reconstruction error in Eq.~\eqref{eq:error} as
\begin{align}
  \Bbk{\norm{\tilde\rho_V-\rho}^2}
  = \f1n \sum_\ell \sp{\bk{\chi_{V\ell}|\rho_\ell}
    - \bk{\rho_\ell|\N_{V\ell}|\rho_\ell}},
  \label{eq:error_simp}
\end{align}
where $\ket{\rho_\ell}\equiv\sum_m \rho_{\ell m}\ket{m}$, and similarly $\ket{\chi_{V\ell}}\equiv\sum_m \chi^V_{\ell m} \ket{m}$ is a vector of the scalars $\chi^V_{\ell m}$ defined by
\begin{align}
  \chi^V_{LM} &\equiv
  \sum_\ell \obk{\N_{V\ell}|\D_M|\I g_{L\ell}}, \\
  g_{L\ell} &\equiv \sum_{m,m'}
  \obk{T_{L,m+m'}|T_{\ell m}T_{\ell m'}} \op{m}{m'}, \\
  \I &\equiv \sum_m \p{-1}^m \op{-m}{m}, \\
  \D_M &\equiv \sum_{m,m'} \delta_{M,m'-m} \op{mm'}.
\end{align}
Here $g_{L\ell}$ is essentially a matrix of transition operator product coefficients (see Appendix \ref{sec:trans_prod}), and $\D_M$ simply picks off the $M$-th diagonal of the matrix it acts on.
Maximizing the reconstruction error in Eq.~\eqref{eq:error_simp} over all $\rho$ with $\tr\rho=1$ leads to the bound in Eq.~\eqref{eq:bound} with
\begin{align}
  \epsilon_V^2 \equiv \sum_{\ell>0} \sp{\f14 \bk{\chi_{V\ell}|\N_{V\ell}^{-1}|\chi_{V\ell}}
    + \f1d \tr\p{\N_{V\ell}}}.
\end{align}
Note that the maximum of Eq.~\eqref{eq:error_simp} may generally occur at an unphysical ``state'' $\rho$ with negative eigenvalues.
In principle, there is therefore room for improvement on the bound in Eq.~\eqref{eq:bound} by maximizing reconstruction error over the restricted domain of states with a non-negative spectrum.

@@

  \ket{\chi_{V\ell}}
  - \sp{\N_{V\ell} + \I N_{V\ell}^* \I} \ket{\rho_{V\ell}^\star}
  = \ket{\chi_{V\ell}}
  - 2 \N_{V\ell} \ket{\rho_{V\ell}^\star}

@@

@@

  \f12 \N_{V\ell}^{-1} \ket{\chi_{V\ell}},

@@

  = \f{\epsilon_V^2}{n},

@@

  \epsilon_V^2
  \equiv \sum_{\ell>0} \f14 \bk{\chi_{V\ell}|\N_{V\ell}^{-1}|\chi_{V\ell}}
  + \sp{\f{\bk{\chi_{V,0}|0}}{\sqrt{d}} - \f{\bk{0|\N_{V,0}|0}}{d}}
  = \sum_{\ell>0} \sp{\f14 \bk{\chi_{V\ell}|\N_{V\ell}^{-1}|\chi_{V\ell}}
    + \f1d \tr\p{\N_{V\ell}}}.

@@

In principle, there is therefore room for improvement on the bound in Eq.~\eqref{eq:bound_SM} by maximizing reconstruction error over the restricted domain of states with a non-negative spectrum.
